Study of Intra- and Inter-Job Interference with Different Job Allocations

### 2016-07-08 submission.tex
change some reference format

Network contention between concurrently running jobs on HPC systems is a primary cause of performance variability. Optimizing job allocation and avoiding network sharing are hence crucial to alleviate the potential degradation in performance. In order to do these effectively, an understanding of the interaction between applications, their communication patterns, and the system architecture are required. In this work, we choose three representative HPC applications from DOE Design Forward Project and conduct detailed simulations of high-performance network topologies to analyze both intra- and inter-job interference. By scrutinizing the communication behaviors of these applications, we identify relationships between these behaviors and the possible interference introduced by different job allocation scenarios. Our comprehensive analyses in this work illuminate a path towards job-communication-pattern-aware HPC resource allocation.

@@

\bibliographystyle{IEEEtran}
\bibliography{./reference}

>>>>

Network contention between concurrently running jobs on HPC systems 
is a primary cause of performance variability. 
Optimizing job allocation and avoiding network sharing are 
hence crucial to alleviate the potential performance degradation. 
In order to do these effectively, 
an understanding of the interference among the concurrently running jobs, 
their communication patterns, and the network contention are required. 
In this work, we choose three representative HPC applications from 
DOE Design Forward Project and conduct detailed simulations of 
on a Torus network model to analyze both intra- and inter-job interference. 
By scrutinizing the communication behaviors of these applications, 
we identify relationships between these behaviors and 
the possible interference introduced by different job placement policies. 
Our comprehensive analyses in this work illuminate a path 
towards job-communication-pattern-aware HPC resource allocation.

@@

\bibliographystyle{IEEEtran}
\bibliography{IEEEabrv, reference}
